Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-17 latex/comp_or.tex
Plots order change

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p1data20.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]		
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p2data20.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);		
		\end{tikzpicture}

	\end{center}
	\caption{ {\it mpShims} performance with $1.2 \times volume$. }
	\label{fig:mpShimsdata20}
\end{figure}

Observing Figure \ref{fig:mpShimsdata20}, it may be noticed that the best number of processes for {\it Scenario 1} (the closest to the {\it Utopia}) is \textbf{6}. For {\it Scenario 2}, the best number is \textbf{4}.

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p1data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p2data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}
	\end{center}
	\caption{{\it mpShims} performance with $1.5 \times volume$.}
	\label{fig:mpShimsdata50}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p1data20.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p2data20.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}
	\end{center}
	\caption{{\it mpACO} performance with $1.2 \times volume$.}
	\label{fig:mpACOdata20}
\end{figure}

\begin{figure}[H]

	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p1data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p2data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}
	\end{center}
	\caption{{\it mpACO} performance with $1.5 \times volume$.}
	\label{fig:mpACOdata50}
\end{figure}

Observing figures \ref{fig:mpShimsdata20}, \ref{fig:mpShimsdata50}, \ref{fig:mpACOdata20}, \ref{fig:mpACOdata50}, it may be noticed that the best overall number of processes for all scenarios is \textbf{?}, because in average it is the number that most of the times is closer to the {\it Utopia} red bullet.

>>>>

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpShims computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p1data20.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
		\begin{axis}[
			myplotstyle,
			xlabel={\bf mpACO computation times (s)},
			ylabel={\bf Score},
			]
			\addplot+[
			only marks,	
			nodes near coords = {\numProcs{}},
			visualization depends on = {value \thisrow{np} \as \numProcs},						
			]
			table[x=time, y=score, col sep=comma] {./csv/ACO_p1data20.csv};
		\end{axis}
		\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
	\end{tikzpicture}

	\end{center}
	\caption{ Scenario 1 performances with $1.2 \times volume$. }
	\label{fig:scenario1data20}
\end{figure}

Observing Figure \ref{fig:scenario1data20}, it may be noticed that the best number of processes for {\it Scenario 1} (the closest to the {\it Utopia}) is \textbf{6}. For {\it Scenario 2}, the best number is \textbf{4}.

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpShims computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p1data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpACO computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p1data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}

	\end{center}
	\caption{ Scenario 1 performances with $1.5 \times volume$. }
	\label{fig:scenario1data50}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpShims computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p2data20.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpACO computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p2data20.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}

	\end{center}
	\caption{ Scenario 2 performances with $1.2 \times volume$. }
	\label{fig:scenario2data20}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpShims computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p2data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpACO computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p2data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}

	\end{center}
	\caption{ Scenario 2 performances with $1.5 \times volume$. }
	\label{fig:scenario2data50}
\end{figure}

%Observing figures \ref{fig:mpShimsdata20}, \ref{fig:mpShimsdata50}, \ref{fig:mpACOdata20}, \ref{fig:mpACOdata50}, it may be noticed that the best overall number of processes for all scenarios is \textbf{?}, because in average it is the number that most of the times is closer to the {\it Utopia} red bullet.
